Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-10-11 manuscript/supporting_information.Rmd
minor changes for final MEE files

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \usepackage{graphicx}
bibliography: ~/Dropbox/Bibliography/MicroMeso.bib
csl: components/ecology.csl

@@

# Supporting Information

@@

##  Hierarchical Bayesian models for vital rates
Here we describe the statistical models in complete detail, including full description of the Bayesian models and Stan code for each model. We write each model as three parts: (1) a data model (likelihood), (2) a process model, and (3) a parameter model. We then combine these three models to write the posterior and joint distributions as a single model statement. Following the full model expression we provide the Stan code that directly corresponds the statement of posterior and joint distributions. Note that Stan uses standard deviations ($\sigma$) to specify distributions rather than variances ($\sigma^2$)  In our expressions of the posterior and joint distributions we use general probability notation where [.] represents some unspecified distribution. We do this for clarity of model presentation. All prior distributions are defined in the parameter model sections. For clarity, we avoid subscripting species.

@@

>>>>

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \usepackage{graphicx}
   - \usepackage{morefloats}
bibliography: ~/Dropbox/Bibliography/MicroMeso.bib
csl: components/ecology.csl

@@

\begin{center}
\textbf{\Large{Supporting Information Appendix S1}}  \\
A.T. Tredennick, M.B. Hooten, \& P.B. Adler, ``Do we need demographic data...''  \\
\emph{Methods in Ecology and Evolution}
\end{center}

@@

##  Hierarchical Bayesian models for vital rates
Here we describe the statistical models in complete detail, including full description of the Bayesian models and Stan code for each model. We write each model as three parts: (1) a data model (likelihood), (2) a process model, and (3) a parameter model. We then combine these three models to write the posterior and joint distributions as a single model statement. Following the full model expression we provide the Stan code that directly corresponds the statement of posterior and joint distributions. Note that Stan uses standard deviations ($\sigma$) to specify distributions rather than variances ($\sigma^2$). In our expressions of the posterior and joint distributions we use general probability notation where [.] represents some unspecified distribution. We do this for clarity of model presentation. All prior distributions are defined in the parameter model sections. For clarity, we avoid subscripting species.

@@

\begin{table}[ht]
\centering
\caption {Statistical tests of model comparisons at different forecast horizons. Table shows results from one-sided t-tests for the particular comparison.}
\begin{scriptsize}
\begin{tabular}{lllrrrlr}
  \hline
comparison & performance\_measure & test\_type & test\_statistic & df & p\_value & species & horizon \\ 
  \hline
climate IPM vs. climate QBM & rho & t & -0.305 & 167.000 & 0.619 & PASM & 1.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.262 & 149.000 & 0.397 & POSE & 1.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.538 & 129.000 & 0.704 & HECO & 1.000 \\ 
  climate IPM vs. climate QBM & rho & t & -1.231 & 129.000 & 0.890 & BOGR & 1.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.679 & 150.000 & 0.751 & PASM & 2.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.260 & 132.000 & 0.602 & POSE & 2.000 \\ 
  climate IPM vs. climate QBM & rho & t & -2.385 & 115.000 & 0.991 & HECO & 2.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.843 & 114.000 & 0.799 & BOGR & 2.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.109 & 129.000 & 0.543 & PASM & 3.000 \\ 
  climate IPM vs. climate QBM & rho & t & -2.423 & 112.000 & 0.992 & POSE & 3.000 \\ 
  climate IPM vs. climate QBM & rho & t & -2.043 & 98.000 & 0.978 & HECO & 3.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.609 & 96.000 & 0.272 & BOGR & 3.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.497 & 108.000 & 0.310 & PASM & 4.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.276 & 94.000 & 0.608 & POSE & 4.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.677 & 82.000 & 0.750 & HECO & 4.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.059 & 78.000 & 0.477 & BOGR & 4.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.095 & 91.000 & 0.538 & PASM & 5.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.492 & 79.000 & 0.688 & POSE & 5.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.894 & 70.000 & 0.813 & HECO & 5.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.186 & 65.000 & 0.573 & BOGR & 5.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.365 & 75.000 & 0.642 & PASM & 6.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.613 & 66.000 & 0.729 & POSE & 6.000 \\ 
  climate IPM vs. climate QBM & rho & t & -2.420 & 59.000 & 0.991 & HECO & 6.000 \\ 
  climate IPM vs. climate QBM & rho & t & 0.047 & 54.000 & 0.481 & BOGR & 6.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.309 & 62.000 & 0.621 & PASM & 7.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.390 & 53.000 & 0.651 & POSE & 7.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.752 & 50.000 & 0.772 & HECO & 7.000 \\ 
  climate IPM vs. climate QBM & rho & t & -1.131 & 44.000 & 0.868 & BOGR & 7.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.353 & 54.000 & 0.637 & PASM & 8.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.862 & 47.000 & 0.803 & POSE & 8.000 \\ 
  climate IPM vs. climate QBM & rho & t & -0.326 & 43.000 & 0.627 & HECO & 8.000 \\ 
  climate IPM vs. climate QBM & rho & t & -2.599 & 37.000 & 0.993 & BOGR & 8.000 \\ 
   \hline
\end{tabular}
\end{scriptsize}
\end{table}

\begin{table}[ht]
\centering
\caption {Statistical tests of model comparisons at different forecast horizons. Table shows results from one-sided t-tests for the particular comparison. Note the reverse order of comparisons relative to Table S23.}
\begin{scriptsize}
\begin{tabular}{lllrrrlr}
  \hline
comparison & performance\_measure & test\_type & test\_statistic & df & p\_value & species & horizon \\ 
  \hline
climate QBM vs. climate IPM & rho & t & 0.305 & 167.000 & 0.381 & PASM & 1.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.262 & 149.000 & 0.603 & POSE & 1.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.538 & 129.000 & 0.296 & HECO & 1.000 \\ 
  climate QBM vs. climate IPM & rho & t & 1.231 & 129.000 & 0.110 & BOGR & 1.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.679 & 150.000 & 0.249 & PASM & 2.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.260 & 132.000 & 0.398 & POSE & 2.000 \\ 
  climate QBM vs. climate IPM & rho & t & 2.385 & 115.000 & 0.009 & HECO & 2.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.843 & 114.000 & 0.201 & BOGR & 2.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.109 & 129.000 & 0.457 & PASM & 3.000 \\ 
  climate QBM vs. climate IPM & rho & t & 2.423 & 112.000 & 0.008 & POSE & 3.000 \\ 
  climate QBM vs. climate IPM & rho & t & 2.043 & 98.000 & 0.022 & HECO & 3.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.609 & 96.000 & 0.728 & BOGR & 3.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.497 & 108.000 & 0.690 & PASM & 4.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.276 & 94.000 & 0.392 & POSE & 4.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.677 & 82.000 & 0.250 & HECO & 4.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.059 & 78.000 & 0.523 & BOGR & 4.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.095 & 91.000 & 0.462 & PASM & 5.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.492 & 79.000 & 0.312 & POSE & 5.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.894 & 70.000 & 0.187 & HECO & 5.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.186 & 65.000 & 0.427 & BOGR & 5.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.365 & 75.000 & 0.358 & PASM & 6.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.613 & 66.000 & 0.271 & POSE & 6.000 \\ 
  climate QBM vs. climate IPM & rho & t & 2.420 & 59.000 & 0.009 & HECO & 6.000 \\ 
  climate QBM vs. climate IPM & rho & t & -0.047 & 54.000 & 0.519 & BOGR & 6.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.309 & 62.000 & 0.379 & PASM & 7.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.390 & 53.000 & 0.349 & POSE & 7.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.752 & 50.000 & 0.228 & HECO & 7.000 \\ 
  climate QBM vs. climate IPM & rho & t & 1.131 & 44.000 & 0.132 & BOGR & 7.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.353 & 54.000 & 0.363 & PASM & 8.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.862 & 47.000 & 0.197 & POSE & 8.000 \\ 
  climate QBM vs. climate IPM & rho & t & 0.326 & 43.000 & 0.373 & HECO & 8.000 \\ 
  climate QBM vs. climate IPM & rho & t & 2.599 & 37.000 & 0.007 & BOGR & 8.000 \\ 
   \hline
\end{tabular}
\end{scriptsize}
\end{table}
